\vfill World of Warcraft's New Way to Get You Hooked

### 2013-02-13 paper.tex
Facts and Research Question sections cleaned up and up to spec

World of Warcraft is an incredibly popular game with over 10 million subscribers. \cite{WoWPlayerCount} Players of World of Warcraft spend an average of 22 hours per week playing. \cite{PlayerMotivations} As of July 2011 World of Warcraft is free to play provided the player is willing to accept some restrictions. None of those restrictions hinder the number of hours one can play. \cite{StarterEditionFAQ} Multiple studies have shown that time spent playing a MMORPG, like World of Warcraft, correlates to addiction level in some individuals. \cite{ProblemUsageAmongHighlyEngagedPlayers}\cite{JustAComputerGameRight} The intensity with which many players play World of Warcraft or other MMORPGs has led to multiple deaths. \cite{SnowlyDeath}\cite{ShawnDeath}

@@

\section{Research Question}
Is Blizzard's switch to World of Warcraft: Starter Edition ethical? \\
Blizzard's switch could precipitate an ``outbreak'' of videogame addiction leading to terrible incidents \cite{SnowlyDeath} and a sharp decline in the sale of games. With fewer games being purchased, software companies that focus on games would suffer.

>>>>

World of Warcraft is an incredibly popular game with over 10 million subscribers. \cite{WoWPlayerCount} Players of World of Warcraft spend an average of 22 hours per week playing. \cite{PlayerMotivations} World of Warcraft is free to play provided the player is willing to accept some restrictions. None of those restrictions hinder the number of hours one can play. \cite{StarterEditionFAQ} Multiple studies have shown that time spent playing a MMORPG, like World of Warcraft, correlates to addiction level in some individuals. \cite{ProblemUsageAmongHighlyEngagedPlayers}\cite{JustAComputerGameRight} The intensity with which many players play World of Warcraft or other MMORPGs has led to multiple deaths. \cite{SnowlyDeath}\cite{ShawnDeath}

@@

\section{Research Question}
Is Blizzard's use of World of Warcraft: Starter Edition ethical? \\
World of Warcraft: Starter Edition could precipitate an ``outbreak'' of videogame addiction leading to terrible incidents. \cite{SnowlyDeath} Deaths and addiciton linked to World of Warcraft would cause a sharp decline in the sale of games. Blizzard would suffer and be forced to lay off software engineers working on its products.
